Peer Assessment 1
========================================================

This assignment contents multiple parts. The entire assignment is completed in a single R markdown document which was processed by knitr and be transformed into an HTML file.

Loading and preprocessing the data
```{r}
# Load the data 
step <- read.csv("./activity.csv",stringsAsFactors=FALSE)
stepping<-na.omit(step)

```

Histogram of the total number of steps taken each day
```{r Histogram of the total number of steps taken each day}
# Load plyr package
library("plyr")

# Create df for "steps counting"
count<-ddply(stepping, .(date), summarize, steps=sum(steps)) 

# Load ggplot2 package
library("ggplot2")

# Histogram of the total number of steps taken each day
qplot(date, data=count, weight=steps)+ geom_histogram(colour="white", fill="red",binwidth=.5)+ theme(axis.text.x = element_text(angle=90)) + xlab("Days") + ylab("Steps")

```

The mean and median total number of steps taken per day
```{r}
median(count$steps)
mean(count$steps)

```

Average daily activity pattern
```{r Average daily activity pattern}
# Time series plot  of the 5-minute interval (x-axis) and the average number of steps taken
count_int<-ddply(stepping, .(interval), summarize, steps=mean(steps))
ggplot( count_int, aes( interval, steps )) + geom_line() + ylab("average number of steps taken")

#Interval with maximum number of steps
count_int$interval[which.max(count_int$steps)]

```

Imputing missing values
```{r Histogram of the total number of steps taken each day - Imputed}
# Imputing missing values
# Report the total number of missing values in the dataset
sum(is.na(step))

# Filling in all of the missing values in the dataset
library("mice")
library("lattice")

# Imputation with "mice" function
step_imp = mice(step)

# Histogram of the total number of steps taken each day (after imputation)
count_imp<-ddply(complete(step_imp), .(date), summarize, steps=sum(steps))
qplot(date, data=count_imp, weight=steps)+ geom_histogram(colour="white", fill="blue",binwidth=.5)+ theme(axis.text.x = element_text(angle=90)) + xlab("Days") + ylab("Steps")

# The mean and median total number of steps taken per day
median(count_imp$steps)
mean(count_imp$steps)

# The impact of imputing missing data on the estimates of the total daily number of steps
ifelse(median(count$steps) < median(count_imp$steps), "Median of imputing dataset is bigger than previous one", "Median of imputing dataset is smaller than previous one")
ifelse(mean(count$steps) < mean(count_imp$steps), "Mean of imputing dataset is bigger than previous one", "Mean of imputing dataset is smaller than previous one")
```

The differences in activity patterns between weekdays and weekends
```{r Activity patterns between weekdays and weekends}
# the dataset with two levels, indicating whether a given date is a weekday or weekend day.
week<-complete(step_imp)
week$date<-weekdays(as.Date(week$date))

week$date[week$date=="nede¾a"|week$date=="sobota"]<- "weekend"
week$date[week$date=="pondelok"|week$date=="utorok"|week$date=="streda"|week$date=="štvrtok"|week$date=="piatok"] <- "weekday"

# Time series plot  of the 5-minute interval (x-axis) and the average number of steps taken

xyplot(steps ~ interval| date,data=week,type="l",layout=c(1,2))

```



End of first peer assignment!
